Taming the Bitvector Bestiary

### 2024-07-28 paper.tex
chore: add stub for new section I'll write now
chore: write about bitwise reasoning
chore: nuke acknowledgements

\createtodoauthor{grosser}{pairedOneLightBlue}
\createtodoauthor{authorTwo}{pairedTwoDarkBlue}
\createtodoauthor{authorThree}{pairedThreeLightGreen}
\createtodoauthor{authorFour}{pairedFourDarkGreen}
\createtodoauthor{authorFive}{pairedFiveLightRed}
\createtodoauthor{authorSix}{pairedSixDarkRed}

@@

\input{outline/01-introduction.tex}
\input{outline/01-LeanSAT.tex}
\input{outline/02-arbitrary-width.tex}
\input{outline/03-Automaton-Decision-Procedure.tex}
\input{outline/04-Non-complete-automation.tex}
\input{outline/05-Evaluation.tex}
\input{outline/06-Related-Work.tex}

@@

%% Acknowledgments
\begin{acks}                            %% acks environment is optional
                                        %% contents suppressed with 'anonymous'
  %% Commands \grantsponsor{<sponsorID>}{<name>}{<url>} and
  %% \grantnum[<url>]{<sponsorID>}{<number>} should be used to
  %% acknowledge financial support and will be used by metadata
  %% extraction tools.
  This material is based upon work supported by the
  \grantsponsor{GS100000001}{National Science
    Foundation}{http://dx.doi.org/10.13039/100000001} under Grant
  No.~\grantnum{GS100000001}{nnnnnnn} and Grant
  No.~\grantnum{GS100000001}{mmmmmmm}.  Any opinions, findings, and
  conclusions or recommendations expressed in this material are those
  of the author and do not necessarily reflect the views of the
  National Science Foundation.
\end{acks}

>>>>

\createtodoauthor{grosser}{pairedOneLightBlue}
\createtodoauthor{sid}{pairedThreeLightGreen}
\createtodoauthor{authorTwo}{pairedTwoDarkBlue}
\createtodoauthor{authorFour}{pairedFourDarkGreen}
\createtodoauthor{authorFive}{pairedFiveLightRed}
\createtodoauthor{authorSix}{pairedSixDarkRed}

@@

\input{outline/01-introduction.tex}
\input{outline/01-API.tex}
\input{outline/01-LeanSAT.tex}
\input{outline/02-arbitrary-width.tex}
\input{outline/03-Automaton-Decision-Procedure.tex}
\input{outline/04-Non-complete-automation.tex}
\input{outline/05-Evaluation.tex}
\input{outline/06-Related-Work.tex}

@@

%% Acknowledgments
% \begin{acks}                            %% acks environment is optional
%                                         %% contents suppressed with 'anonymous'
%   %% Commands \grantsponsor{<sponsorID>}{<name>}{<url>} and
%   %% \grantnum[<url>]{<sponsorID>}{<number>} should be used to
%   %% acknowledge financial support and will be used by metadata
%   %% extraction tools.
%   This material is based upon work supported by the
%   \grantsponsor{GS100000001}{National Science
%     Foundation}{http://dx.doi.org/10.13039/100000001} under Grant
%   No.~\grantnum{GS100000001}{nnnnnnn} and Grant
%   No.~\grantnum{GS100000001}{mmmmmmm}.  Any opinions, findings, and
%   conclusions or recommendations expressed in this material are those
%   of the author and do not necessarily reflect the views of the
%   National Science Foundation.
% \end{acks}
